A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-12 manuscript.Rmd
closes #52

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
The machine learning community has begun to use simulated data to test models and their implementation [@braiekTestingMachineLearning2020].
Beyond checking the technical side of the model, simulation is also beneficial on a conceptual level [@axelrodAdvancingArtSimulation1997].
Simulated data lets you verify that the data you expect to gather and the analysis you plan fit together.
No matter which analytic strategy you plan, it comes with assumptions and a simulation forces you to address these assumptions more directly than simply thinking about them.
If you identify unrealistic assumptions, you can either violate these assumptions and see if the analytic strategy is robust or modify the analytical approach to address them.
We will show an example using structural equation modeling (SEM) for our Machiavellism example.
However, the general process applies to any statistical model, but the simulation here is specific to our hypothetical research question.
One has to make many educated guesses to simulate data that closely matches your expectation.
These guesses strongly depend on the study you are planning, and there cannot be a one fits all solution.
The analytic strategy (i.e. SEM) often gives you a hint about how to simulate data.

@@

PAC works well within this reproducible framework.
First, the preregistration becomes a part of the reproducible repository.
It is part of the set of version-controlled files and provides transparency about when the preregistration file, data files, and code files were changed over the course of a research project.
If code was version-controlled and tagged (see Section [Git]) before data collection, all deviations from the preregistration or any post-hoc additions that were performed after data collection are transparent and are visible and comparable in the version history.

One way to ensure that you can expect your analysis to work with real data is to simulate data.
A data simulation allows you to verify that the code runs error-free and lets you form more realistic expectations about the estimates' correctness and precision.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `r minn$n_obs` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `r round((est_diff - true_diff)*100/true_diff, 2)`%.
These results are also visualized in Figure \@ref(fig:simulation-plot).
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Dynamic document generation combines code and text, enabling you to explain your reasoning.
See the section on [R Markdown] for an example of a dynamic document generation paradigm.

>>>>

There are probably few things as frustrating as realizing that the data that you gathered cannot answer the research question you had in mind.
A step to prevent unpleasant surprises is to simulate data.
The machine learning community has begun to use simulated data to test models and their implementation [@braiekTestingMachineLearning2020].
Beyond checking the technical side of the model, simulation is also beneficial on a conceptual level [@axelrodAdvancingArtSimulation1997].
Simulated data lets you verify that the data you expect to gather and the analysis you plan fit together.
Beyond ensuring that the code runs without technical error and it lets you form more realistic expectations about the estimates' correctness and precision.
No matter which analytic strategy you plan, it comes with assumptions and a simulation forces you to address these assumptions more directly than simply thinking about them.
If you identify unrealistic assumptions, you can either violate these assumptions and see if the analytic strategy is robust or modify the analytical approach to address them.
We will show an example using structural equation modeling (SEM) for our Machiavellism example.
However, the general process applies to any statistical model, but the simulation here is specific to our hypothetical research question.
One has to make many educated guesses to simulate data that closely matches your expectation.
These guesses strongly depend on the study you are planning, and there cannot be a one fits all solution.
The analytic strategy (i.e. SEM) often gives you a hint about how to simulate data.

@@

PAC works well within this reproducible framework.

First, the preregistration becomes a part of the reproducible repository.
It is part of the set of version-controlled files and provides transparency about when the preregistration file, data files, and code files were changed over the course of a research project.
If code was version-controlled and tagged (see Section [Git]) before data collection, all deviations from the preregistration or any post-hoc additions that were performed after data collection are transparent and are visible and comparable in the version history.

One way to ensure that you can expect your analysis to work with real data is to simulate data.
We, for example, simulated data for the Machiavellism subscale of the short dark triad (SD3) and analyzed this with structural equation modelling (SEM).
The simulation showed that we have to gather at least `r minn$n_obs` observations per group to archive enough precision and that our solution to a data problem we expect (insufficient measurement invariance) introduces a bias of `r round((est_diff - true_diff)*100/true_diff, 2)`%.
These results are also visualized in Figure \@ref(fig:simulation-plot).
If you went to the trouble to simulate data, we argue that you get a preregistration almost for free.
A preregistration in code describes sufficiently how you want to analyze the data, but ideally, you also convey the why.
Dynamic document generation combines code and text, enabling you to explain your reasoning.
See the section on [R Markdown] for an example of a dynamic document generation paradigm.
In fact, this manuscript and therefore the here presented Machiavialismus example were preregistered as a full manuscript, and you can see the results on real data in section [Reproduce a Project].
